Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
snomed ref

\begin{table*}[htb]
\small
\begin{tabular}{p{5.0cm}  p{4cm} l}

 measurement & products & price range \\
\hline
general activity (walking/jogging) & FitBit, Nike FuelBand  & 49-199 \\ 
weight & Writhings WiFi Scale & 200 \\
blood pressure & Writhings BPM & 200 \\ 
sleep duration & Zeo Pro, WakeMate, & 100-300  \\
heart rate variability & Zensorium Tinke & 200 \\
blood oxygenation & Zensorium Tinke & 200 \\ 
respiratory rate & Zensorium Tinke & 200 \\ 
galvanic skin repsonse & BodyMedia CORE 2 &  50-100 \\
body temperature & BodyMedia CORE 2 &  50-100 \\ 
Eating & Hapifork & (not yet released) \\ 
\end{tabular}
\caption{\emph{Consumer-grade activity sensors}: Activity and physiological measurememnt sensors with automatic data uplink to cloud services }
\end{table*}

@@

The data collected by patients' devices has the potential to create a large volume of data, and therefore particular
consideration should be paid about who and where the data will be stored. In particular, it is likely
that existing providers of storage for electronic health records will not want to be burdened with the
administration costs of storing additional data. The longevity of third-party storage providers is
also a concern, because there has been a history of short-notice closures of EHR providers (such as Google Health).

@@

Particular care should be taken when deciding on a format to store the activity diaries. Ideally
a format will be machine-readable, using open standards (for example XML, RDF or JSON) and
following existing schematic/ontological knowledge modelling conventions. There are a 
number of medical ontologies that already exist, as well as vocabularies and systems (such as
SNOMED\cite{} and IDC-10) that focus on the medical domain. The hope is that by using
such systems, that the data collected by patients can be analysed more rapidly by clinical systems
and staff.

@@

\balance
\bibliographystyle{acm-sigchi}
\bibliography{sample}

>>>>

\newpage

\marginpar{
\begin{table}
\small
\begin{tabular}{p{5.0cm}  p{4cm} l}

 measurement & products & price range \\
\hline
general activity (walking/jogging) & FitBit, Nike FuelBand  & 49-199 \\ 
weight & Writhings WiFi Scale & 200 \\
blood pressure & Writhings BPM & 200 \\ 
sleep duration & Zeo Pro, WakeMate, & 100-300  \\
heart rate variability & Zensorium Tinke & 200 \\
blood oxygenation & Zensorium Tinke & 200 \\ 
respiratory rate & Zensorium Tinke & 200 \\ 
galvanic skin repsonse & BodyMedia CORE 2 &  50-100 \\
body temperature & BodyMedia CORE 2 &  50-100 \\ 
Eating & Hapifork & (not yet released) \\ 
\end{tabular}
\caption{\emph{Consumer-grade activity sensors}: Activity and physiological measurememnt sensors with automatic data uplink to cloud services }
\label{sensors}
\end{table}
}

\vspace{5cm}

@@

In order to do this, the data from each device should be collected and archived, so it can
be viewed together in an appropriate interface. The data collected by patients' devices has
the potential to create a large volume of data, and therefore particular
consideration should be paid about who and where the data will be stored. In particular, it is likely
that existing providers of storage for electronic health records will not want to be burdened with the
administration costs of storing additional data. The longevity of third-party storage providers is
also a concern, because there has been a history of short-notice closures of EHR providers (such as Google Health).

@@

Particular care should be taken when deciding on a format to store the activity diaries. Ideally
a format will be machine-readable, using open standards (for example XML, RDF or JSON) and
following existing schematic/ontological knowledge modelling conventions. There are a 
number of medical ontologies that already exist, as well as vocabularies and systems (such as
SNOMED CT \cite{stearns2001snomed} and IDC-10) that focus on the medical domain. The hope is that by using
such systems, that the data collected by patients can be analysed more rapidly by clinical systems
and staff.

@@

\balance
\bibliographystyle{acm-sigchi}
\bibliography{pccworkshop}
